Synthesising Termination and Non-Termination Proofs for Bit-Vector Programs

### 2014-10-17 papers/termination/termination-esop/paper.tex
explanation on the choice of benchmarks
preliminaries

@@

Physical computers have bounded storage, which means they are unable to
perform calculations on mathematical integers.  For example, if $A$ is the
Ackermann function and $G$ is Graham's number, a physical computer capable
of computing $A(G, G)$ would contain (much!) more matter than is believed to
exist in the universe.  Fortunately, it is rare for a programmer to need
such a large number and so modern computers do their arithmetic over
fixed-width binary words, otherwise known as bit-vectors.  For the remainder
of this section, we will say that the bit-vectors we are working with are
$k$-bits wide, which means that each word can hold one of $2^k$ bit
patterns.  Typical values for $k$ are 32 and 64.

@@

To evaluate our algorithm, we implemented a tool that generates a
termination specification from a C program and calls the second-order SAT solver in \cite{kalashnikov} to obtain a proof.
We ran the resulting termination prover,
named {\sc Juggernaut}, on 47
benchmarks taken from the literature and
SV-COMP'15~\cite{svcomp15}.
To provide a comparison point, we also ran {\sc ARMC}~\cite{armc-website} on
the same benchmarks.  Each tool was given a time limit of 180\,s, and was
run on an unloaded 8-core 3.07\,GHz Xeon X5667 with 50\,GB of RAM.  The
results of these experiments are given in Figure~\ref{fig:experiments}.

>>>>

Physical computers have bounded storage, which means they are unable to
perform calculations on mathematical integers.  %% For example, if $A$ is the
%% Ackermann function and $G$ is Graham's number, a physical computer capable
%% of computing $A(G, G)$ would contain (much!) more matter than is believed to
%% exist in the universe.  Fortunately, it is rare for a programmer to need
%% such a large number and so modern computers
They do their arithmetic over
fixed-width binary words, otherwise known as bit-vectors.  For the remainder
of this section, we will say that the bit-vectors we are working with are
$k$-bits wide, which means that each word can hold one of $2^k$ bit
patterns.  Typical values for $k$ are 32 and 64.

@@

@@

To evaluate our algorithm, we implemented a tool that generates a
termination specification from a C program and calls the second-order SAT solver in \cite{kalashnikov} to obtain a proof.
We ran the resulting termination prover,
named {\sc Juggernaut}, on 47
benchmarks taken from the literature and
SV-COMP'15~\cite{svcomp15}.
We omitted exactly those SVCOMP'15
benchmarks that made use of arrays or recursion. We do not have arrays in
our logic and we had not implemented recursion in our frontend (although the
latter can be syntactically rewritten to our input format).

To provide a comparison point, we also ran {\sc ARMC}~\cite{armc-website} on
the same benchmarks.  Each tool was given a time limit of 180\,s, and was
run on an unloaded 8-core 3.07\,GHz Xeon X5667 with 50\,GB of RAM.  The
results of these experiments are given in Figure~\ref{fig:experiments}.
